\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx,float,wrapfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{bibhacks}
\usepackage[nowarn]{glossaries}
%\documentstyle[nips13submit_09,times,art10]{article} % For LaTeX 2.09

% Define acronyms
\newacronym{pmf}{PMF}{Probabilistic Matrix Factorization}
\newacronym{lda}{LDA}{Latent Dirichlet Allocation}
\newacronym{bpf}{BPF}{Bayesian Poisson Factorization}
\newacronym{hpf}{HP}{Heirarchical Poisson Factorization}
\newacronym{cf}{CF}{Collaborative Filtering}

\title{Probabilistic Matrix Factorization}


\author{ 
  Mert Terzihan \\
  Department of Computer Science\\
  Brown University\\
  Providence, RI 02912 \\
  \texttt{mert\_terzihan@brown.edu}
  \And
  Gabriel Barth-Maron \\
  Department of Computer Science \\
  Brown University \\
  Providence, RI 02912 \\
  \texttt{gabriel\_barth-maron@brown.edu}\\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}


\maketitle
\begin{abstract}
This is an abstract.
\end{abstract}

\section{Introduction}

\section{Related Work}

\Gls{pmf} has been used extensively and to success in \gls{cf} systems \cite{koren2009matrix}. Some notable techniques that have been used in this area are: Probabilistic Latent Semantic Analysis (PLSA) \cite{hofmann1999probabilistic}, Multinomial Principal Component Analysis \cite{buntine2002variational}, \acrfull{lda} \cite{lda}, and \acrfull{bpf} \cite{gopalan2013scalable}.

\Gls{lda} is one of the most widely used matrix factorization technique in
\gls{cf} systems. As studied in \cite{lda} and \cite{discrete-pca},
one can observe that LDA is equivalent to factorizing a matrix
probabilistically using a graphical model representation. Instead of dealing with a co-occurence matrix, we will try to propose a model and
a learning algorithm to factorize a matrix where each cell is a rating of an item
by a particular user. Therefore, in addition to LDA, we would also like to generate
ratings that have been assigned by users to each item. 

In \cite{Argwal-fDLA} a method based on LDA is proposed to produce personalized recommendations.
However, fLDA takes into account much more information about the user, i.e. age, 
gender, zipcode, etc. We are going to use a simpler model, which relies on
much less personal information. We will be using only the ratings 
that have been given by the users to specific items.

A LDA-based probabilistic matrix factorization models is proposed in
\cite{conf/icdm/ShanB10}, however instead of using discrete distribution
for generating ratings, it has placed a Gaussian distribution over the user's
ratings. In our investigation we hope to relax this assumption and look into
models that are not necessarily Gaussian.

\acrfull{hpf} \cite{gopalan2013scalable} is a recent \gls{pmf} technique that
extends the Gamma-Poisson (GaP) model proposed by \cite{canny2004gap}.
In addition to \gls{hpf}, the authors of \cite{gopalan2013scalable} also
proposed \gls{bpf}, which sets the rate parameter for the Gamama distributions for
all users and items. It is believed that Poisson factorization better captures
preferences in \gls{cf} tasks. This is proven empirically, as \gls{hpf} and \gls{bpf} perform better than \gls{lda} across a variety of \gls{cf} tasks, including movie recommendation \cite{gopalan2013scalable}.


\section{Latent Dirichlet Allocation}

\section{Bayesian Poisson Factorization}

\section{Results}

\section{Conclusions}

\section{Future Remarks}

\bibliographystyle{plain}
\bibliography{main}
\end{document}
